Random Forests", OAs

### 2023-11-14 src/oa_RF.Rmd
oa.rf

@@

@@

```{r}
# London = Islington 
oa.sf <- st_as_sf(oa.gb)

help1 <- st_filter( la.sf, cities.sf) %>% as_tibble %>% dplyr::select(LAD21CD) %>% 
  left_join(df, by = c("LAD21CD"="ladcd")) %>% dplyr::select(LAD21CD, year, n)

help1 <- st_filter( la.sf, cities.sf) %>% as_tibble %>% dplyr::select(LAD21NM,LAD21CD) %>% 
  mutate(cities = c("Leicester",
                    "Bristol",
                    "Manchester",
                    "Liverpool",
                    "Sheffield",
                    "Birmingham",
                    "Leeds",
                    "London",
                    "Edinburgh",
                    "Glasgow"))

dist$dist.city.name <- names(dist)[apply(dist[,1:9], MARGIN = 1, FUN = which.min)]
help2 <- dist %>% left_join(help1, by = c("dist.city.name" = "cities")) %>% 
  rename(nearest.city.LAD21CD = LAD21CD) %>% 
  dplyr::select(ladcd, nearest.city.LAD21CD)

df <- df %>% drop_na() %>% group_by(year) %>% 
  mutate(n.slag = lag.listw(knn.l, n)) %>% 
  group_by(ladcd) %>% 
  mutate(n.l.slag = dplyr::lag(n.slag, n=1, order_by=year),
         n.lag = dplyr::lag(n, n=1, order_by = year)) %>% 
  left_join(help2, by = c("ladcd" = "ladcd"))

@@

# Join with distance and area
df <- df %>% left_join(dist, by = c("oa11cd" = "oa11cd")) %>% 
  left_join(oa.gb@data, by = c("oa11cd" = "id")) %>% 
  relocate(area, .after = n) %>% 
  mutate(area = area / 1000000,
         density = n / area) %>% 
  relocate(density, .after = area)
sapply(df, function(x) sum(is.na(x)))
```

>>>>

# Complete panel
df <- df %>% filter(!is.na(oa11cd)) %>% 
  complete(oa11cd, year) %>% 
  replace(is.na(.), 0)

@@

# Join with distance and area
df <- df %>% left_join(dist, by = c("oa11cd" = "oa11cd")) %>% 
  left_join(oa.gb@data, by = c("oa11cd" = "id")) %>% 
  relocate(area, .after = n) %>% 
  mutate(area = area / 1000000,
         density = n / area) %>% 
  relocate(density, .after = area)

@@

```{r}
## THIS DROPS L999999... AND NI, WHICH NEEDS TO BE FIXED
df <- df %>% filter(!is.na(area))

# London = Islington 
oa.sf <- st_as_sf(oa.gb)
cities.sf <- st_as_sf(cities, coords = c("long", "lat"))
cities.sf <- st_set_crs(cities.sf, 4326)

help1 <- st_filter(oa.sf, cities.sf) %>% as_tibble %>% dplyr::select(id) %>% 
  left_join(df, by = c("id"="oa11cd")) %>% dplyr::select(id, year, n)

sf_use_s2(FALSE)
help1 <- st_filter( oa.sf, cities.sf) %>% as_tibble %>% dplyr::select(id) %>% 
  mutate(cities = c("Leicester",
                    "Bristol",
                    "Manchester",
                    "Liverpool",
                    "Sheffield",
                    "Birmingham",
                    "Leeds",
                    "London",
                    "Edinburgh",
                    "Glasgow"))

# too slow
#dist$dist.city.name <- names(dist)[apply(dist[,2:11], MARGIN = 1, FUN = which.min)]

dist <- dist %>% mutate(dist.city.name = names(.)[max.col(.[2:11]*-1)+1L])

help2 <- dist %>% left_join(help1, by = c("dist.city.name" = "cities")) %>% 
  rename(nearest.city.oa11cd = id) %>% 
  dplyr::select(oa11cd, nearest.city.oa11cd)

sf_use_s2(FALSE)
oa.c <- st_centroid(oa.sf)
kn <- knearneigh(oa.c, k = 5)
knn <- knn2nb(kn, row.names = NULL, sym = FALSE)
knn.l <- nb2listw(knn)

df <- df %>% drop_na() %>% 
  group_by(year) %>% 
  mutate(n.slag = lag.listw(knn.l, n)) %>% 
  group_by(oa11cd) %>% 
  mutate(n.l.slag = dplyr::lag(n.slag, n=1, order_by=year),
         n.lag = dplyr::lag(n, n=1, order_by = year)) %>% 
  left_join(help2, by = c("oa11cd" = "oa11cd"))

@@
